A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
Updated the code coverage metric

Running this code results on average in \CorpusMeanExprCoverage package code
coverage. The code coverage was computed for each package using
Covr\footnote{\url{ https://github.com/r-lib/covr}}, the R code coverage tool.

>>>>

For each package we use its runnable code to compute the package code
coverage\footnote{Computed using \url{ https://github.com/r-lib/covr}}. On
average, across the \CorpusPackages packages, it is \CorpusMeanExprCoverage.
